---
title: "R Project 1 - Hello R"
author: "Joshua Boehm"
date: "Due September 8th"
output: html_document
--- 



### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The Dataaurus Dozen data contains 12 datasets in a dataframe consisting of 1846 rows and 3 variables: dataset, which indicates which data set the data is sourced; x, for x-values; and y, for y-values.

### Exercise 2

#### The Dino Plot Visualized

The data visualized shows a picutre of a dinosaur with a certain set of summary statistics, e.g mean, standard deviation, et cetera that should be noted.

```{r plot-dino, fig.height=5, fig.width=5}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#### The Correlation Coefficient

This measurement shows a ***linear*** relationship between the x and y values. The nearer the value is to 0, the lesser the linear relationship.

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

#### The Star Plot Visualized

This data visualized maintains the nearly identical summary statistics as the Dino Plot above, but has a drastically different visual representaiton.


```{r plot-star, fig.height=5, fig.width=5}
star_data <- datasaurus_dozen %>% filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) + geom_point()
```

#### The Correlation Coefficient
 
```{r cor-star}
dino_data %>% summarize(r = cor(x,y))
```

Here we see that the ***linear*** relationship of the data is equal to the above plot. This expresses the same linear relationship as the dinosaur despite having a markedly different visualization of the data.

### Exercise 4

#### The Circle Plot Visualized

Here again we find yet another visualization that's vastly different from the prior two, yet has nearly identical summary statistics.

```{r plot-circle, fig.height=5, fig.width=5}
circle_data <- datasaurus_dozen %>% filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x=x,y=y)) + geom_point()
```

#### The Correlation Coefficient

```{r cor-circle}
dino_data %>% summarize(r = cor(x,y))
```

As could be expected, there is nearly no ***linear*** relationship between the variables x and y, and that relationship is exactly the same as the rest.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
