---
title: "R Project 1 - Hello R"
author: "Joshua Boehm"
date: "Due September 8th"
output: 
  html_document: 
    fig_width: 6
    fig_height: 6
    theme: simplex
    highlight: kate
--- 

&nbsp;
&nbsp;
&nbsp;

## Load packages


```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

&nbsp;

## Exercise 1

&nbsp;

The Datasaurus Dozen contains 13 datasets (including the datasaur itself) in a data frame consisting of 1846 rows and 3 variables: dataset, indicating from which data set the data is sourced; x, for x-values; and y, for y-values. These data sets have the same summary statistics, i.e. x/y mean, x/y standard deviation, and the Pearson's correlation.

```{r}
 datasaurus_dozen %>% count(dataset) %>% print(26)
```

&nbsp;

In the table below, we see these standard measures are equal to the hundredths for all 13 of the data sets.

```{r}
datasaurus_dozen %>% group_by(dataset) %>% summarize('x-mean' = mean(x = x),'y-mean' = mean(x = y), 'x sd' = sd(x), 'y sd' = sd(x = y), "Pearson's Correlation" = cor(x,y)) %>% print()
```

&nbsp;

## Exercise 2

&nbsp;

#### The Dino Plot Visualized

The data visualized shows a picutre of a dinosaur with a certain set of summary statistics, e.g mean, standard deviation, et cetera that should be noted.

```{r plot-dino, fig.height=5, fig.width=5}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#### The Correlation Coefficient

This measurement shows a ***linear*** relationship between the x and y values. The nearer the value is to 0, the lesser the linear relationship.

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

&nbsp;

## Exercise 3

&nbsp;

#### The Star Plot Visualized

This data visualized maintains the nearly identical summary statistics as the Dino Plot above, but has a drastically different visual representaiton.


```{r plot-star, fig.height=5, fig.width=5}
star_data <- datasaurus_dozen %>% filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) + geom_point()
```

#### The Correlation Coefficient
 
```{r cor-star}
dino_data %>% summarize(r = cor(x,y))
```

Here we see that the ***linear*** relationship of the data is equal to the above plot. This expresses the same linear relationship as the dinosaur despite having a markedly different visualization of the data.

&nbsp;

## Exercise 4

&nbsp;

#### The Circle Plot Visualized

Here again we find yet another visualization that's vastly different from the prior two, yet has nearly identical summary statistics.

```{r plot-circle, fig.height=5, fig.width=5}
circle_data <- datasaurus_dozen %>% filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x=x,y=y)) + geom_point()
```

#### The Correlation Coefficient

```{r cor-circle}
dino_data %>% summarize(r = cor(x,y))
```

As could be expected, there is nearly no ***linear*** relationship between the variables x and y, and that relationship is exactly the same as the rest.

&nbsp;

## Exercise 5

&nbsp;

These are all 13 data sets visualized and colored.
```{r fig.width=7, fig.height=13}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols 
  theme(legend.position = "none")
```

These values represent the Pearson's Correlation values for all the data sets.

```{r}
datasaurus_dozen %>% group_by(dataset) %>% summarize(r = cor(x, y)) %>% print(26)
```

